\LARGE \bf An Algorithm to Reduce a Supervisor Demonstrations for DAgger in Learning From Demonstrations[v9]

### 2015-07-28 paper.tex
some of Jeff's comments

\title{\LARGE \bf
An Algorithm to Reduce Supervisor Demonstrations for DAgger in Learning From Demonstrations[v9] }

@@

\begin{abstract}
For robot control problems where the dynamics of the environment and the reward function are unknown, one technique is to learn a policy that attempts to match a supervisor's demonstration . A state of the art method in learning from demonstration is known as Dataset Aggregation, or DAgger. DAgger treats learning from demonstration as a supervised learning problem.The algorithm iteratively trains a policy on labeled data and then estimates states the robot is likely to encounter by executing the trained policy and has the supervisor tell the robot what controls it should have applied. Some successes of DAgger have been achieving state of the art performance on both Mario and Atari video game benchmarks, flying a quadcopter through a forest and teaching a robot to follow verbal instructions. One potential limitation though of DAgger is that it requires the supervisor to label the control for every state the robot visits during training, which can be expensive and tedious if the supervisor is a human. We propose estimating where the train policy is likely to mis-predict the supervisor's control, which we define as area of risk and then only having the supervisor label these states. Areas of risk can occur if the state is far from training data or if it has been incorrectly classified during the supervised learning. We propose identifying these areas via a modified version of the One Class SVM, which is used to estimate a level set of the distribution trained on. Then only states outside of this boundary are queried. Initial results suggest \todo{once we polish the experiments tomorrow and Wednesday}

@@

\section{Related Work}
The field of learning from demonstration has achieved state of the art performance in a variety of areas within robotics \cite{argall2009survey}. Abbeel et al. used an iLQR controller around helicopter trajectories demonstrated by an expert to successfully learn a series of aerobatics stunts \cite{abbeel2007application}. Billard and Matari used a hierarchy of neural networks on video data and tracking markers to imitate a human arms movements on a 37 degree of freedom humaniod robot \cite{billard2001learning}. Schulman et al. used a non-linear warping, thin plate splines, on collected trajectories of a human controlling a PR2 and tying knots with a rope. Then transferred the demonstrations to the new unseen initial configurations of the rope~\cite{schulman2013case}.

@@

Our proposed method trains a policy, $\pi_{\theta_k}$, but also estimates where the policy is likely to accurately predict the competent controller's control,which we define as the region of low risk.  In the statistics community, a known property is that estimators are function will mis-classify if they are evaluated at points not in the distribution sampled from.Techniques such as importance sampling use this results to train estimators on data drawn from a different distribution \cite{tokdar2010importance}.  Thus, we try to estimate the level set of the training distribution, which is explained in \ref{sec:level} and only have the competent controller provide labels when the robot leaves this boundary. Furthermore to avoid entering pathological states that are far from the competent controller's demonstrations, we terminate the roll-out when it is a certain distance or risk factor from the decision boundary, which is given by $r(\bx) = \sum_i^n \alpha_i \bx_i k(\bx_i,\bx)-\rho$. The risk threshold, $r_0$, is user defined based on the task.

@@

\section{Experiments}
\subsection{Driving Example}
A common benchmark in RL is a car driving around a track avoiding other cars \cite{argall2009survey}. In our driving simulator a car is driven around a rectangular track and has orange cars placed on the track as well that need to be dodged. If the car falls off the track, it is placed back on to the center. Our control space $u = \lbrace -15^\circ, 0, 15^\circ \rbrace$. Our supervisor is a solver that uses state space search through the driving simulator to plan the next control.

We have the supervisor drive around the track 3 times and then collect the raw images observed. We use a Gaussian Pyramids to down sample the images to $125 \times 125$ RGB pixels and then extract Histogram of Oriented Gradients (HOG) features using OpenCV. For both DAgger and SHEATH, we use a Linear Support Vector Machine (SVM) as the policy representation, with the regularization term on the slack variable $\gamma=0.01$, which was set via cross validation on the initial training examples from our expert.. We initialized both Dagger and SHEATH with two expert demonstrations for each level. For the optimization of Eq. \ref{eq:dual_sup} in SHEATH we used a radial basis function as well for the kernel with a bandwidth of $\lambda=0.01$ and $\nu = 0.95$ to account for $95\%$ of the training distribution.

We compare performance in terms of optimization of the underlying cost function $c(\bx,\bu)$, which is the sum of the number of times the car left the track and the number of times the car collided with the other cars on the track. Initial results averaged over 1 level shown in Fig.  suggest an $75\%$ reduction in the number of queries needed for SHEATH compared to DAgger.

@@

\begin{figure}[t!]
\centering
\includegraphics[width=8cm, height=6cm]{figures/dagger_sheath_no_cars.png}
\caption{ We compare performance in terms of optimization of the underlying cost function $c(\bx,\bu)$, which is the sum of the number of times the car left the track and the number of times the car collided with the other cars on the track. Initial results averaged over 1 level shown suggest an $75\%$ reduction in the number of queries needed for SHEATH compared to DAgger.  }

>>>>

\title{\LARGE \bf
An Algorithm to Reduce a Supervisor Demonstrations for DAgger in Learning From Demonstrations[v9] }

@@

\begin{abstract}
For robot control problems where the dynamics of the environment and the reward function are unknown, one technique is to learn a policy that attempts to match a supervisor's demonstration, also known as learning from demonstration . A state of the art method in learning from demonstration is known as Dataset Aggregation, or DAgger. DAgger treats learning from demonstration as an iterative supervised learning problem.The algorithm alternates between training a policy on labeled data and then acquiring labels on states the robot is likely to encounter by executing the trained policy and having the supervisor tell the robot what controls it should have applied. Some successes of DAgger have been achieving state of the art performance on both Mario and Atari video game benchmarks, flying a quadcopter through a forest and teaching a robot to follow verbal instructions. One potential limitation though of DAgger is that it requires the supervisor to label the control for every state the robot visits during training, which can be expensive and tedious if the supervisor is a human. We propose estimating where the train policy is likely to mis-predict the supervisor's control, which we define as areas of risk and then only having the supervisor label these states. Areas of risk can occur if the state is far from training data or if it has been incorrectly classified during the supervised learning step. We propose identifying these areas via a modified version of the One Class SVM, which is used to estimate a level set of the distribution trained on. Then only states outside of this boundary are queried. Initial results suggest \todo{once we polish the experiments tomorrow and Wednesday}

@@

\section{Related Work}
The field of learning from demonstration has achieved state of the art performance in a variety of areas within robotics \cite{argall2009survey}. Abbeel et al. used an iLQR controller around helicopter trajectories demonstrated by an expert to successfully learn a series of aerobatics stunts \cite{abbeel2007application}. Billard and Matari used a hierarchy of neural networks on video data and tracking markers to imitate a human arms movements on a 37 degree of freedom humaniod robot \cite{billard2001learning}. Schulman et al. used a non-linear warping, thin plate splines, on collected trajectories of a human controlling a PR2 and tying knots with a rope then transferred the demonstrations to the new unseen initial configurations of the rope~\cite{schulman2013case}.

@@

Our proposed method trains a policy, $\pi_{\theta_k}$, but also estimates where the policy is likely to accurately predict the competent controller's control,which we define as the region of low risk.  In the statistics community, a known property is that estimators are function will likely mis-classify if they are evaluated at points not in the distribution sampled from.Techniques such as importance sampling use this results to train estimators on data drawn from a different distribution \cite{tokdar2010importance}.  Thus, we try to estimate the level set of the training distribution, which is explained in \ref{sec:level} and only have the competent controller provide labels when the robot leaves this boundary. Furthermore to avoid entering pathological states that are far from the competent controller's demonstrations, we terminate the roll-out when it is a certain distance or risk factor from the decision boundary, which is given by $r(\bx) = \sum_i^n \alpha_i \bx_i k(\bx_i,\bx)-\rho$. The risk threshold, $r_0$, is user defined based on the task.

@@

\section{Experiments}
\subsection{Driving Example}
A common benchmark in RL is a car driving around a track avoiding other cars \cite{argall2009survey}. In our driving simulator, the car must stay on a rectangular track and dodge the orange cars that are on the track as well. If the car falls off the track, it is placed back on to the center. The car's control space $u = \lbrace -15^\circ, 0, 15^\circ \rbrace$ or 3 discrete commands that change the angle of the car. The internal state space of the car is xy-coordinates and the angle it is facing. Our supervisor is a solver that uses state space search through the driving simulator to plan the next control.

We have the supervisor drive around the track 2 times and then collect the raw images observed. We use a Gaussian Pyramids to down sample the images to $125 \times 125$ RGB pixels and then extract Histogram of Oriented Gradients (HOG) features using OpenCV. For both DAgger and SHEATH, we use a Linear Support Vector Machine (SVM) as the policy representation, with the regularization term on the slack variable $\gamma=0.01$, which was set via cross validation on the initial training examples from our expert. For the optimization of Eq. \ref{eq:dual_sup} in SHEATH we used a radial basis function as well for the kernel with a bandwidth of $\lambda=0.01$ and $\nu = 0.95$ to account for $95\%$ of the training distribution.

We compare performance in terms of minimization of the underlying cost function $c(\bx,\bu)$, which is the sum of the number of times the car left the track and the number of times the car collided with the other cars on the track, versus the number of queries made to the supervisor. Initial results averaged over 1 level shown in Fig.  suggest an $75\%$ reduction in the number of queries needed for SHEATH compared to DAgger.

@@

\begin{figure}[t!]
\centering
\includegraphics[width=8cm, height=6cm]{figures/dagger_sheath_no_cars.png}
\caption{ We compare performance in terms of optimization of the underlying cost function $c(\bx,\bu)$, which is the sum of the number of times the car left the track and the number of times the car collided with the other cars on the track. Initial results averaged over 1 level shown suggest an $75\%$ reduction in the number of queries needed for SHEATH compared to DAgger. \todo{Run this over many trials}  }
